Workflow for Ecov Recruitment Analysis

### 2024-01-20 Ecov_study/recruitment_functions/Workflow_Ecov_Recruitment_Project.Rmd
bias in time series results
bias.assessment code and plots added, Rmd  in recruitment_functions main directory updated

4. Look at bias in SSB, Recr, Fbar **bias_assessment.R**
   + specify gradient and SE tolerance at top (these were appended to AIC dataframe outputs in the step above)
   + specify results directory (where runs are), directory where to save plots, and a suffix to append at end of file name (to distinguish plots for different cases)
   + regression trees are done to determine factors associated RE in recruitment, SSB, and Fbar
      + looks like sigmaR is the only factor that matters for all 3 metrics
      + this script produces plots summarizing relative error (RE) over all years, the last 10 years, and the final year

5. Look at bias in parameter estimates **bias_parameters.R**
   + SR_a, SR_b, sigmaR, rho_R, sigmaEcov, rho_Ecov
   + also grabbing catchability (logit_q), selectivity (logit_selpars), catch_paa_pars, and index_paa_pars parameters so i don't have to pass through results again

>>>>

4. Look at bias in SSB, Recr, Fbar **bias_assessment.R**
   + specify gradient and SE tolerance at top (these were appended to AIC dataframe outputs in the step above)
   + specify results directory (where runs are), directory where to save plots, and a suffix to append at end of file name (to distinguish plots for different cases)
   + regression trees are done to determine factors associated RE in recruitment, SSB, and Fbar
      + looks like sigmaR is the only factor that matters for all 3 metrics
      + this script produces plots summarizing relative error (RE) over all years, the last 10 years, and the final year
   + Runtime is slooooow (and code is inefficient--feel free to tighten it up)
   + **<span style="color: blue;">STATUS: done for beta unstandardized; </span>**

5. Look at bias in parameter estimates **bias_parameters.R**
   + SR_a, SR_b, sigmaR, rho_R, sigmaEcov, rho_Ecov
   + also grabbing catchability (logit_q), selectivity (logit_selpars), catch_paa_pars, and index_paa_pars parameters so i don't have to pass through results again
   + Runtime ...pending
   + **<span style="color: blue;">STATUS: pending beta unstandardized; </span>**
